Quotient maps and configuration spaces of hard disks

### 2022-02-10 manuscript/main.tex
figure app1 completed

	\section{Relations between the $z_{\vec{k}}$}
	\label{sec:descriptor_proofs}

	This section provides proofs and supporting materials to show the relations among the descriptors. Let $\vec{x}$ and $\vec{a}$ respectively be the coordinates of a vector in the $xy$-coordinate system and $a_1a_2$-coordinate system. Let $\mat{T}$ be the forward coordinate transformation matrix such that $\vec{a} = \mat{T} \vec{x}$ and $\vec{x} = \mat{T}^{-1} \vec{a}$.

	The procedure to calculate the descriptors $z_{\vec{k}}$ is illustrated in Fig.\ \ref{fig:app1}. For a configuration $\config{p}$ whose coordinates are given in $xy$-coordinate system, the first step is to find the corresponding coordinates of the disks in the $a_1a_2$-coordinate system, and define the function $f(\vec{a})$ using Eq.\ \ref{eq:f}. Observe that the resulting function will be the same for each $n!$ permutations of the disk labels. Then, the complex coefficients of the infinite expansion in Eq.\ \ref{eq:f} are calculated using the orthogonality of complex exponentials as shown in Eq.\ \ref{eq:c_k}. The final step is then to take the modulus of these complex coefficients using Eq.\ \ref{eq:z_k}. Observe that the complex coefficients and the descriptors are sorted with respect to the distance of $\vec{k}$ from the origin. Moreover, observe that the complex coefficients $c_{\vec{k}}$ and $c_{-\vec{k}}$ have the same descriptors $z_{\vec{k}}$ for a given configuration.

	\begin{figure}
		\centering
		\includegraphics[width=1.0\columnwidth]{app1.eps}
		\caption{$3!$ permutations of a given configuration will result in the same function $f(\vec{a})$ after using Eq.\ \ref{eq:f}. The complex coefficients are calculated using Eq.\ \ref{eq:c_k}. Finally, the descriptors $z_{\vec{k}}$ are then defined as the modulus of the complex coefficients.}
		\label{fig:app1}
	\end{figure}

	The complex coefficients $c_{\vec{k}}$ is equal to $c^{\ast}_{-\vec{k}}$ where $^{\ast}$ denotes complex conjugate.
	\begin{proof}
		Let $\config{p}$ be a configuration and $\vec{p}$ be the coordinates of the disks in $a_1a_2$-coordinate system.
		\begin{align*} 
		c_{\vec{k}}(\config{p}) &=  \sum_{j=1}^{n} \exp{(-2\pi \rmi \vec{k} \cdot \vec{p}_j)} \nonumber \\ 
		&= \left\{ \sum_{j=1}^{n} \exp{(2\pi \rmi \vec{k} \cdot \vec{p}_j)} \right\}^{\ast} \nonumber \\
		&= \left\{ \sum_{j=1}^{n} \exp{[-2\pi \rmi (-\vec{k} \cdot \vec{p}_j)]} \right\}^{\ast} \nonumber \\
		&= c_{-\vec{k}}^{\ast}(\config{p})
		\end{align*}
	\end{proof}

	The descriptors $z_{\vec{k}}(\config{p}) = z_{-\vec{k}}(\config{p})$.
	\begin{proof}
		Using the fact that $c_{\vec{k}} = c^{\ast}_{-\vec{k}}$
		\begin{align*} 
		z_{\vec{k}}(\config{p}) =  \sqrt{c_{\vec{k}}(\config{p}) c_{\vec{k}}^\ast(\config{p})} = \sqrt{c^{\ast}_{-\vec{k}}(\config{p}) c_{-\vec{k}}(\config{p})} = z_{-\vec{k}}(\config{p})
		\end{align*}
	\end{proof}

@@

	Finally, the descriptors $\hat{z}_{\vec{k}}$ in Eq.\ \ref{eq:z_hat_k} are not all independent. Let $\vec{x}$ and $\vec{a}$ respectively be the coordinates of a vector in the $xy$-coordinate system and $a_1a_2$-coordinate system. Let $\mat{T}$ be the forward transformation matrix such that $\vec{a} = \mat{T} \vec{x}$ and $\vec{x} = \mat{T}^{-1} \vec{a}$.

>>>>

	\section{Relations between the $z_{\vec{k}}$}
	\label{sec:descriptor_proofs}
	\red{
	This section provides proofs and supporting materials to show the relations among the descriptors. The procedure to calculate the descriptors $z_{\vec{k}}$ is illustrated in Fig.\ \ref{fig:app1}. For a configuration $\config{p}$ whose coordinates are given in $xy$-coordinate system, the first step is to find the corresponding coordinates of the disks in the $a_1a_2$-coordinate system, and define the function $f(\vec{a})$ using Eq.\ \ref{eq:f}. Observe that the resulting function will be the same for each $n!$ permutations of the disk labels. Then, the complex coefficients of the infinite expansion in Eq.\ \ref{eq:f} are calculated using the orthogonality of complex exponentials as shown in Eq.\ \ref{eq:c_k}. The final step is then to take the modulus of these complex coefficients using Eq.\ \ref{eq:z_k}. Observe that the complex coefficients and the descriptors are sorted with respect to the distance of $\vec{k}$ to the origin. Moreover, observe that the complex coefficients $c_{\vec{k}}$ and $c_{-\vec{k}}$ have the same descriptors $z_{\vec{k}}$ for a given configuration.}

	\begin{figure}
		\centering
		\includegraphics[width=1.0\columnwidth]{app1.eps}
		\caption{\red{$3!$ permutations of a given configuration will result in the same function $f(\vec{a})$ after using Eq.\ \ref{eq:f}. The complex coefficients are calculated using Eq.\ \ref{eq:c_k}. Finally, the descriptors $z_{\vec{k}}$ are then defined as the modulus of the complex coefficients.}}
		\label{fig:app1}
	\end{figure}

	\red{The complex coefficients $c_{\vec{k}}$ is equal to $c^{\ast}_{-\vec{k}}$ where $^{\ast}$ denotes complex conjugate.}
	\begin{proof}
		\red{Let $\config{p}$ be a configuration and $\vec{p}$ be the coordinates of the disks in $a_1a_2$-coordinate system.
		\begin{align*} 
		c_{\vec{k}}(\config{p}) &=  \sum_{j=1}^{n} \exp{(-2\pi \rmi \vec{k} \cdot \vec{p}_j)} \nonumber \\ 
		&= \left\{ \sum_{j=1}^{n} \exp{(2\pi \rmi \vec{k} \cdot \vec{p}_j)} \right\}^{\ast} \nonumber \\
		&= \left\{ \sum_{j=1}^{n} \exp{[-2\pi \rmi (-\vec{k} \cdot \vec{p}_j)]} \right\}^{\ast} \nonumber \\
		&= c_{-\vec{k}}^{\ast}(\config{p})
		\end{align*}}
	\end{proof}

	\red{Let $\config{p}$ be a configuration and $\vec{p}$ be the coordinates of the disks in $a_1a_2$-coordinate system.}
	\begin{proof}
		\red{Using the fact that $c_{\vec{k}} = c^{\ast}_{-\vec{k}}$
		\begin{align*} 
		z_{\vec{k}}(\config{p}) =  \sqrt{c_{\vec{k}}(\config{p}) c_{\vec{k}}^\ast(\config{p})} = \sqrt{c^{\ast}_{-\vec{k}}(\config{p}) c_{-\vec{k}}(\config{p})} = z_{-\vec{k}}(\config{p})
		\end{align*}}
	\end{proof}

@@

	Finally, the descriptors $\hat{z}_{\vec{k}}$ in Eq.\ \ref{eq:z_hat_k} are not all independent. Let $\vec{x}$ and $\vec{a}$ respectively be the coordinates of a point in the $xy$-coordinate system and $a_1a_2$-coordinate system as shown in Fig.\ \ref{fig:app2}. \red{}

	Let $\mat{T}$ be the forward transformation matrix such that $\vec{a} = \mat{T} \vec{x}$ and $\vec{x} = \mat{T}^{-1} \vec{a}$.

	\begin{figure}
		\centering
		\includegraphics[width=0.6\columnwidth]{app2.eps}
		\caption{caption here.}
		\label{fig:app2}
	\end{figure}
